\chapter{Player Commands}
\label{app:commands}
{\scriptsize
\begin{longtable}{p{4cm}p{9cm}}
add $<$display$>$ & Adds a display. Use from telnet connection. \\ 
apply $<$string$>$ & Applies top object in inventory {\em if} you give a string. \\ 
archs & ??? \\ 
bell $<$player$>$ & Makes that player's display beep. \\ 
berzerk & Toggles berzerk status. \\ 
bind & Used to bind commands to keys. \\ 
brace & Toggles brace status. While braced you will not move. \\ 
cast $<$spell$>$ & Readies named spell. \\ 
clearinfo & Clears the text screen. \\ 
disarm & Executes a disarming action in facing direction. \\ 
dm & Player becomes the dm. You character is unsavable after this. \\ 
drop $<$object$>$ & Drops object from player inventory. \\ 
dropall &  Drops all but locked objects in inventory. \\ 
east & Execute a move east. \\ 
examine $<$object$>$ & Examines object, defaults to top object in inventory. \\ 
get & Picks up top object in look window. \\ 
gsay & Sends a message only to members of your party.\\ 
help $<$subject$>$ & Help on subject, defaults to shows list of available help. \\
hiscore & Show list of highest player scores. \\ 
inv-lock & Locks top object in inventory. \\ 
inv-unlock & Unlocks top object in inventory. \\ 
inventory & Lists all objects in inventory in text window. \\ 
invoke $<$spell$>$ $<$string$>$ & Readies, then casts a spell. String is optional \\
keyboard & Toggles buffering of keystrokes. \\ 
last & Not Implemented. \\ 
listen & Changes the level of your hearing. \\ 
malloc & Shows which stuff is taking up how much memory. \\ 
mapinfo & Show information about current map. \\ 
maps & Show status of all active maps. \\
motd & Show message of the day again. \\ 
north & Execute a move north. \\ 
northeast & Ditto to north east. \\  
northwest & Ditto to the north west. \\ 
output-count & No idea what this does. \\ 
output-sync &  No idea what this does. \\
party $<$command$>$ & Set of commands used with simple party system. \\ 
peaceful & Toggle peaceful status. \\ 
pickup $<$command$>$ & Change pickup status by number or value density. \\ 
prepare & Alias for cast command. \\ 
quit & Quit the game with out saving your character. \\ 
ready\_skill $<$skill$>$ & Prepare a skill for use. \\ 
refresh & Refresh all windows in the display. \\ 
rotateinventory & Rotate inventory by 1. \\ 
rotateshoottype & Rotate the range slot by 1. \\ 
rotatespells & Rotate through all known spells alphabetically. \\ 
save & Save your current position and status. \\ 
savewinpos & Save your current window layout. \\ 
say & Say something to all players on your map. \\ 
scroll & Toggle scrolling in the text window. \\ 
search & Execute a search in all nearby squares.\\ 
search-items $<$command$>$ & Change the status of items searched for. \\ 
shout & Send a message to all players regardless of map.\\ 
show & \\ 
showinvicon & Toggle status of invicon in inventory window. \\ 
skills & Show all available skills, experience categories and level.\\ 
south & Execute a move south.\\ 
southeast & Ditto to southeast. \\ 
southwest & Ditto to southwest. \\ 
sstable & Does something?? \\ 
stay & \\ 
strength $<$integer$>$ & Old command. Now useless. \\
strings & Shows the status of shared sting parameters. \\ 
sync $<$integer$>$ & Change sync value to integer. \\ 
take & Alias for pickup. \\ 
tell $<$who$>$ $<$msg$>$ & Tell character who the msg. \\ 
throw & Disabled command. \\ 
time & Gives statistics on packets?? \\ 
title $<$string$>$ & Change your title to string.\\ 
unbind $<$command$>$ & A set of commands to reverse key bindings. \\ 
use\_skill $<$skill$>$ $<$string$>$ & Ready, then use a skill. String is optional. \\
version & Print out all the contributors to \cf .\\ 
west & Execute a move west. \\ 
who & Show what players are currently logged on. \\
wimpy $<$percent$>$ & Auto-matically run away when hp$<$\%$\times$Max hp. \\ 
\end{longtable}
}
